Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-05-07 paper/ms.tex
adding references

Lyman-$\alpha$ emitting galaxies (LAEs) have become in the last decade a 
central topic in studies of structure formation in the Universe. The
reason is the diverse range of fields where they are helpful. LAEs can
be used as probes of reionization, tracers of large scale structure,
signposts for low metallicity stellar populations and markers of the
the galaxy formation process through cosmic history.

@@

Some theoretical approaches to this problem have been based on a
forward modelling. Starting from the DM halo population, the
corresponding intrinsic star formation properties are infered and
statistics such as the luminosity function, the correlation function
and the equivalent width distributions. Such modelling has been
implemented from analytic considerations, semi-analytic models and
full N-body hidrodynamical simulations.

@@

Our model is based on the predictions of a large volume high
resolution N-body simulation describing the gravitational dynamics of
dark matter. We do not have an strong bias towards the theoretical
expectation of what the mass of the dark matter halo hosting the
galaxy should be.  Instead, we fully explore the parameter space of
our simplified model. The only cut we impose is that observed LAEs do
not reside in dark matter halos with masses less than 10$^{10}$hMsun
[citation].

>>>>

Lyman-$\alpha$ emitting galaxies (LAEs) have become in the last decade a 
central topic in studies of structure formation in the Universe. They 
are helpful in a diverse range of fields. LAEs can
be used as probes of reionization \citep{Dijkstra11}, tracers of
large scale structure \citep{Koehler2007}, 
signposts for low metallicity stellar populations and markers of the
the galaxy formation process through cosmic history \citep{ForeroRomero2012}.

@@

Some theoretical approaches to this problem have been based on a
forward modelling. Starting from the DM halo population, the
corresponding intrinsic star formation properties are infered and
statistics such as the luminosity function, the correlation function
and the equivalent width distributions. Such modelling has been
implemented from analytic considerations, semi-analytic models and
full N-body hidrodynamical simulations \citep{ForeroRomero2011}.

@@

Our model is based on the predictions of a large volume high
resolution N-body simulation describing the gravitational dynamics of
dark matter. We do not have an strong bias towards the theoretical
expectation of what the mass of the dark matter halo hosting the
galaxy should be.  Instead, we fully explore the parameter space of
our simplified model. The only cut we impose is that observed LAEs do
not reside in dark matter halos with masses less than 10$^{10}$
\hMsun [citation].
